Untitled

### 2025-02-27 script/r/draft.Rmd
merge geo controls

destert_africa <- crop(desert_wgs84, africa_extent)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, desert_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, elevation_adm2)

@@

plot(precipitation_africa, main = "Precipitation Map of Africa", col = viridis(100), breaks = seq(0, 3000, by = 100))

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, precipitation_adm2)

@@

plot(temp_mean_africa, main = "temp_mean Map of Africa", col = rev(heat.colors(100)), breaks = seq(0, 50, by = 1))

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, temp_mean_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, temp_max_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, temp_min_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_2, mountain_adm2)

@@

>>>>

desert_africa <- crop(desert_wgs84, africa_extent)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, NAME_2, desert_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, NAME_2, elevation_adm2)

@@

plot(precipitation_africa, main = "Precipitation Map of Africa", col = rev(viridis(100)))

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, NAME_2, precipitation_adm2)

@@

plot(temp_mean_africa, main = "temp_mean Map of Africa", col = rev(heat.colors(100)))

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, NAME_2, temp_mean_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, NAME_2, temp_max_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, NAME_2, temp_min_adm2)

@@

  country_results <- regions %>%
    as.data.frame() %>%
    rename(iso = GID_0) %>%
    select(iso, NAME_1, NAME_2, mountain_adm2)

@@

```{r}
data_final_r <- readRDS("data/data_rds/data_final_r.rds")

desert_adm1 <- readRDS("data/data_rds/geo_ctrl/desert_adm1.rds")
desert_adm2 <- readRDS("data/data_rds/geo_ctrl/desert_adm2.rds")

desert <- merge(desert_adm1, desert_adm2, by = c("iso", "NAME_1"), all = TRUE)

rm(desert_adm1, desert_adm2)

rounds <- data.frame(round = rep(5:8, each = nrow(desert)))

expanded_data <- desert[rep(1:nrow(desert), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)

data_geo <- expanded_data

rm(desert)

elevation_adm1 <- readRDS("data/data_rds/geo_ctrl/elevation_adm1.rds")
elevation_adm2 <- readRDS("data/data_rds/geo_ctrl/elevation_adm2.rds")

elevation <- merge(elevation_adm1, elevation_adm2, by = c("iso", "NAME_1"), all = TRUE)

rm(elevation_adm1, elevation_adm2)

rounds <- data.frame(round = rep(5:8, each = nrow(elevation)))

expanded_data <- elevation[rep(1:nrow(elevation), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)

data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))

rm(elevation)

mountain_adm1 <- readRDS("data/data_rds/geo_ctrl/mountain_adm1.rds")
mountain_adm2 <- readRDS("data/data_rds/geo_ctrl/mountain_adm2.rds")

mountain <- merge(mountain_adm1, mountain_adm2, by = c("iso", "NAME_1"), all = TRUE)

rm(mountain_adm1, mountain_adm2)

rounds <- data.frame(round = rep(5:8, each = nrow(mountain)))

expanded_data <- mountain[rep(1:nrow(mountain), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)

data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))

rm(mountain)

precipitation_adm1 <- readRDS("data/data_rds/geo_ctrl/precipitation_adm1.rds")
precipitation_adm2 <- readRDS("data/data_rds/geo_ctrl/precipitation_adm2.rds")

precipitation <- merge(precipitation_adm1, precipitation_adm2, by = c("iso", "NAME_1"), all = TRUE)

rm(precipitation_adm1, precipitation_adm2)

rounds <- data.frame(round = rep(5:8, each = nrow(precipitation)))

expanded_data <- precipitation[rep(1:nrow(precipitation), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)

data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))

rm(precipitation)

temp_max_adm1 <- readRDS("data/data_rds/geo_ctrl/temp_max_adm1.rds")
temp_max_adm2 <- readRDS("data/data_rds/geo_ctrl/temp_max_adm2.rds")

temp_max <- merge(temp_max_adm1, temp_max_adm2, by = c("iso", "NAME_1"), all = TRUE)

rm(temp_max_adm1, temp_max_adm2)

rounds <- data.frame(round = rep(5:8, each = nrow(temp_max)))

expanded_data <- temp_max[rep(1:nrow(temp_max), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)

data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))

rm(temp_max)

temp_min_adm1 <- readRDS("data/data_rds/geo_ctrl/temp_min_adm1.rds")
temp_min_adm2 <- readRDS("data/data_rds/geo_ctrl/temp_min_adm2.rds")

temp_min <- merge(temp_min_adm1, temp_min_adm2, by = c("iso", "NAME_1"), all = TRUE)

rm(temp_min_adm1, temp_min_adm2)

rounds <- data.frame(round = rep(5:8, each = nrow(temp_min)))

expanded_data <- temp_min[rep(1:nrow(temp_min), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)

data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))

rm(temp_min)

temp_mean_adm1 <- readRDS("data/data_rds/geo_ctrl/temp_mean_adm1.rds")
temp_mean_adm2 <- readRDS("data/data_rds/geo_ctrl/temp_mean_adm2.rds")

temp_mean <- merge(temp_mean_adm1, temp_mean_adm2, by = c("iso", "NAME_1"), all = TRUE)

rm(temp_mean_adm1, temp_mean_adm2)

rounds <- data.frame(round = rep(5:8, each = nrow(temp_mean)))

expanded_data <- temp_mean[rep(1:nrow(temp_mean), times = 4), ]

expanded_data$round <- rounds$round

expanded_data <- expanded_data %>% distinct(iso, NAME_1, NAME_2, round, .keep_all = TRUE)

data_geo %<>% left_join(expanded_data, by=c("iso", "NAME_1", "NAME_2", "round"))

rm(temp_mean)

data_final_r %<>% left_join(data_geo, by=c("iso", "NAME_1", "NAME_2", "round"))

saveRDS(data_final_r, file="data/data_rds/data_27_05_25.rds")

write_dta(data_final_r, "data/data_dta/data_27_05_25.dta")
```
